The Impact of Anthropogenic Forcing on ENSO Amplitude

### 2021-11-08 presentations/presentation/presentation.tex
fixed some figs, edited presentation

\begin{frame}{ENSO is Becoming Stronger}
  \begin{columns}
    \column{0.5\textwidth}
    \begin{itemize}
    \item Increase in ENSO intensity in both ensembles.
    \item Increase slows down in CESM1 and decreases in CESM2 after around 2050.
      \begin{itemize}
      \item May be caused by aerosol emissions.
      \end{itemize}
    \end{itemize}
    \column{0.5\textwidth}
    \myfig{ff_compare.pdf}{ENSO intensity ensemble mean and standard error for CESM1 and CESM2}{ff_compare}
  \end{columns}
\end{frame}

\begin{frame}{Influence of Aerosols and Greenhouse Gasses}
  \begin{columns}
    \column{0.65\textwidth}
    \begin{itemize}
    \item Influence of each factor on ENSO amplitude.
    \item Increased variance due to greenhouse gas emissions.
    \item Somewhat increased variance from aerosol emissions, but not linear.
    \item Inconclusive results from biomass burning and land use forcing
    \end{itemize}
    \alert{Takeaway:} Human activities are triggering predicted strengthening of ENSO.
    \column{0.5\textwidth}
    \myfig{cesm1_sf.pdf}{Influence of GHG, AER, and BMB forcing on ENSO amplitude in CESM1}{cesm1_sf}
  \end{columns}
\end{frame}

@@

\begin{frame}{Wavelet Analysis}
  \begin{columns}
    \column{0.6\textwidth}
    \begin{itemize}
    \item Separate ENSO record into frequency over time.
    \item Increase in power in late 21\textsuperscript{st} century agrees with previous results.
    \end{itemize}
    \column{0.6\textwidth}
    \myfig{wavelet2.pdf}{Wavelet power spectrum for the Niño 3.4 index in the fully-forced CESM1 and CESM2 ensembles}{wavelet2}
  \end{columns}
\end{frame}

>>>>

\begin{frame}{ENSO is Becoming Stronger}
  \begin{columns}
    \column{0.4\textwidth}
    \begin{itemize}
    \item Increase in ENSO intensity in both ensembles.
    \item Increase slows down in CESM1 and decreases in CESM2 after around 2050.
      \begin{itemize}
      \item May be caused by aerosol emissions.
      \end{itemize}
    \end{itemize}
    \column{0.6\textwidth}
    \myfig{ff_compare.pdf}{ENSO intensity ensemble mean and standard error for CESM1 and CESM2}{ff_compare}
  \end{columns}
\end{frame}

\begin{frame}{Influence of Aerosols and Greenhouse Gasses}
  \begin{columns}
    \column{0.65\textwidth}
    \begin{itemize}
    \item Influence of each factor on ENSO amplitude.
    \item Increased variance due to greenhouse gas emissions.
    \item Somewhat increased variance from aerosol emissions, but not linear.
    \end{itemize}
    \alert{Takeaway:} Human activities are triggering predicted strengthening of ENSO.
    \column{0.5\textwidth}
    \myfig{cesm1_sf_4.pdf}{Influence of GHG, AER, and BMB forcing on ENSO amplitude in CESM1}{cesm1_sf_4}
  \end{columns}
\end{frame}

@@

\begin{frame}{Wavelet Analysis}
  \begin{columns}
    \column{0.5\textwidth}
    \begin{itemize}
    \item Separate ENSO record into changes in period over time.
    \item Increase in power in late 21\textsuperscript{st} century agrees with previous results.
    \item In CESM1, increase in ENSO intensity is mainly strengthening of longer-period cycle.
    \item In CESM2, longer-period ENSO weakens after 2025.
    \end{itemize}
    \column{0.5\textwidth}
    \myfig{wavelet3.pdf}{Wavelet power spectrum for the Niño 3.4 index in the fully-forced CESM1 and CESM2 ensembles}{wavelet2}
  \end{columns}
\end{frame}

% SPLIT UP CONCLUSIONS DISCUSSION

\begin{frame}{Discussion}
  \begin{itemize}
  \item Rising greenhouse gas levels increase Pacific Ocean stratification, strengthening ENSO cycle.
  \item Aerosol influence nonlinear because aerosol levels are not purely increasing.
  \item Stronger ENSO will lead to greater climate variability and extreme weather.
  \item
  \end{itemize}
\end{frame}
